A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Fix wording
Add Alternative representations paragraphs
Add FDD description

In 1986 Bryant\cite{BRYANT86} published a paper of high impact, describing a
\textit{reduced} and \textit{ordered} class of BDDs, so-called \textit{ROBDDs}
(\textit{Reduced Ordered} BDDs) but in literature mostly referred to as
\textit{OBDDs}. OBDDs represent Boolean functions in a \textit{canonical}
form. This results in a compact form and very efficient tests for some properties,
e.g. satisfiability or equivalence\cite{BRYANT86}.

@@

>>>>

In 1986 Bryant\cite{BRYANT86} published a paper of strong impact, describing a
\textit{reduced} and \textit{ordered} class of BDDs, so-called \textit{ROBDDs}
(\textit{Reduced Ordered} BDDs) but in literature mostly referred to as
\textit{OBDDs}. OBDDs represent Boolean functions in a \textit{canonical}
form. This results in a compact form and very efficient tests for some properties,
e.g. satisfiability or equivalence\cite{BRYANT86}.

@@

\paragraph*{Free BDDs}
\mbox{} % workaround to get line break after paragraph

Although the variable ordering problem is well-studied, OBDDs have some severe
limitations for some classes of Boolean functions, regardless of the variable
ordering chosen, e.g. integer multiplication (see Section~\ref{sec:limitations}).
One way researchers tried to overcome this issue is relaxing the variable ordering
requirement. \textit{Free BDDs} (\textit{FDDs}) is one proposed approach. FDDs
do not require the variables in the BDD to be ordered but, instead, require that
each variable only occurs once along any path (starting from the root node).
Hence, FDDS are also referred to as \textit{1-time branching programs}. Moreover,
FDDs have the same desirable algorithmic properties as OBDDs~\cite{BRYANT95}. \tbr

\paragraph*{Zero-Suppressed BDDs}
\mbox{} % workaround to get line break after paragraph

\tbd

\paragraph*{Binary Moment Diagrams}
\mbox{} % workaround to get line break after paragraph

\tbd

\paragraph*{Binary Expression Diagrams}
\mbox{} % workaround to get line break after paragraph

\tbd
